Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ The Online Survey

### 2017-09-18 cloverflow_technical_report/cloverflow_survey_rn.tex
The first complete draft of the research note from the Stack Overflow surveys.

\begin{abstract}
ABSTRACT GOES HERE
\end{abstract}

@@

\subsection{Survey Objective}
The main objective of the survey is to understand the developers' awareness and
experience to outdated code and code licensing on Stack Overflow. It can break
down into the following six research questions.

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ5 (Software licensing issues from Stack Overflow code snippets):}\textit{How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
\end{enumerate}

The first three questions will be answered by
the Stack Overflow answerer survey, while the other three questions will be
answered by the Stack Overflow visitor survey.

@@

\subsubsection{The visitor survey} 
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of
visiting Stack Overflow for solving programming tasks at least once. The
participants were invited to take the survey via five channels. The first
channel is via the first author's social media post (Facebook) where the he
invited friends who are software developers and have experience of copying code
snippets from Stack Overflow to take the survey. The second channel is a popular
technology news and media community in Thailand called \textsf{blognone.com} which
attracts a high number of Thai software developers. The first author posted an
invitation to the visitor survey in a discussion forum mentioning the
requirements to take the survey. The third channel collects answers from the
University of Molise from help of an external researcher. The last two
channels are from a \textsf{comp.lang.java.programmer} Google groups and Software
Engineering Facebook page. The number of participants taken the survey is shown in
Table~\ref{tab:visitors}.

@@

\subsubsection*{RQ4: Where do the developers search for programming solutions?}

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2cm]{0.98\textwidth}{%
		\textit{For RQ4, Stack Overflow is ranked higher than official documentations,
	online repositories, and book as the resource to look for programming
	solutions. Developers rely on Stack Overflow answers because they are easy to
	search for on the web. Moreover, 64\% of the participants reuse code snippets
	from Stack Overflow at least once a week. The copy code from Stack Overflow
    because they can be found easily from search engine, solve similar problems to
    their problems, provide helpful context, and offer voting and accepted answers.}
	}%
} \vspace{0.5cm}

\subsubsection*{RQ5: What are the problems Stack Overflow visitors experiencing
	from reusing code snippets on Stack Overflow?}

@@

The problems from reusing Stack Overflow code snippets (illustrated in
Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions,the code
claims to solve the problem in the question while it does not,  (20 out of 57
$\approx$ 35\%); outdated solutions, i.e.~the code may work with the some older
versions of the library or API, but not the one they are using, (39 out of 57
$\approx$ 68\%); mismatched solutions, i.e.~the code solves the problem in the
question but it is not exactly the right solution for their problem, (40 out of
57 $\approx$ 70\%); and buggy code (1 out of 57 $\approx$ 2\%). Stack Overflow
visitors rarely report the problems back to the discussion threads (as can be
seen in Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32
participants who encounter problems of Stack Overflow snippets, 18 of them
(56\%) never report the problems. As shown in
Figure~\ref{fig:survey_visitor_how_report_problems}, the 14 participants who
reported the problems did so by writing a comment (10), down-voting the answer
(8), contacted the answerer (2), and posting the new and correct answer (2).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2cm]{0.98\textwidth}{%
		\textit{For RQ5, our survey results show that 57 out of 87 Stack Overflow
			visitors find a problem from reusing Stack Overflow code snippets. Ten
			participants experience the problems on more 80\% of the copied snippets and
			sixteen participants face the problems on 40--60\% of the reused code. The
			mostly found problem is a mismatched solution (40), followed by outdated
			solution (39), incorrect solution (20), and buggy code (1). Fifty-six percent
			of the participants never report the problems back to Stack Overflow.}}%
} \vspace{0.5cm}

\subsubsection*{RQ6: Are Stack Overflow visitors aware of the the CC BY-SA 3.0
	license enforced by Stack Overflow?}

As depicted in Figure~\ref{fig:survey_visitor_cc_by-sa}, 74 out of 87 (85\%)
Stack Overflow visitors are not aware, at the time of copying the code, that
Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC
BY-SA 3.0) to content in the posts, including code snippets. As a consequence,
62\% of the visitors never give an attribution, which is required by CC BY-SA
3.0, to a Stack Overflow post they copied the code from (the complete statistics
can be found from Figure~\ref{fig:survey_visitor_attribution-sa}).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{For RQ6, 85\% of the participants are not aware of Stack Overflow CC
	BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
	they copied the code snippets from.}}%
} \vspace{0.5cm}

\subsubsection*{RQ7: How often do Stack Overflow visitors check for software
	licensing issues from code snippets on Stack Overflow?}

Figure~\ref{fig:survey_visitor_original_license} shows that 79\% (69) Stack
Overflow visitors who adopted code from Stack Overflow never check if the code
snippet originated from a different source (e.g. an open source project) with an
incompatible license to their projects.

Sixty-six percent of the participants never check for licensing conflicts at all
when reusing Stack Overflow code (see
Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, possibly due
to their fairly small size of code which might fall under fair use, only 9\% of
the participants experience legal issues by reusing code snippets on Stack
Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{For RQ7, we found that 66\% of the visitors never check for software
	licensing conflicts between Stack Overflow code snippets and their projects.
	However, only 9\% of the participants encountered legal issues.}}%
} \vspace{0.5cm}

@@

\subsection{Internal Validity}
We targeted the participants for the answerer survey based on their Stack Overflow
reputation instead of random sampling. This is because reflects the developers
involvement in asking and answering questions on the site. Thus, our findings
capture awareness and experience of experienced Stack Overflow developers. Moreover,
due to a large number of users on Stack Overflow, we could invite only 607
highly-ranked developers to participate in the study.

We selected the participants for the visitor survey based on convenient sampling which
could suffer from bias and outliers.

\subsection{External Validity} 
While the reputation is a good proxy to reflect the amount of answers the
developers have given, it might not cover all kinds of answerers on Stack
Overflow. The answerers who have lower-reputation than 6,999 were not invited to
our study and their awareness and experience may differ from our findings.

At least 39\% of the participants in the visitor survey are from
\textsf{blognone.com} which is based in Thailand. Due to working culture,
answers from this group of developers may only represent software developers in
Thailand. We alleviate this concern by inviting participants from other groups,
e.g.~University of Molise in Italy, comp.lang.java.programmer, and Software
Engineering Facebook group.

@@

We present the results from online surveys of Stack Overflow answerers and
visitors regarding their awareness and experience of answering and reusing code
snippets on Stack Overflow. We are interested in cloned code in Stack Overflow
answers. Two online surveys have been performed to find out \textit{where} are
the code snippets in Stack Overflow answers from and \textit{how} developers, in
terms of both Stack Overflow answerers and visitors, handle potential problem of
outdated code and software licensing conflicts.

From the answerer's responses, we discovered that code in Stack Overflow answers
is usually written from scratch to answer a question. Nonetheless, there are
some code snippets that are copied from the answerers' personal, open source, or
company projects.

The outdated code on Stack Overflow occurs when the code snippet in an answer is
copied from another location and is no longer up-to-date. The results show that
although the answerers are aware of outdated code in their answers, 19\% of them
rarely or never fix the code.

Regarding the software license, approximately 60\% of the answerers are aware of
Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
the license in their answers nor check for licensing conflicts when they copy
the code from another location and paste in the answer.

>>>>

\begin{abstract}
We performed two online surveys of Stack Overflow answerers and visitors to
assess their awareness to outdated code and software license in Stack Overflow
answerers. The answerer survey targets 607 Stack Overflow users with high
reputation and receives a high response rate of 33\%. While most of the code
snippets in the answers are written from scratch, there are code snippets that
are cloned from the questions, personal or company projects, and also open
source projects. Stack Overflow answerers are aware that some of their snippets
are outdated. However, 19\% of the participants report that they rarely or never
fix the code. At least 98\% of the answerers never include software license in
their snippets and 69\% never check for licensing conflicts with Stack
Overflow's CC BY-SA 3.0 if they copy the code from other sources to Stack
Overflow answers. The visitor survey uses convenient sampling and receives 89
responses. We found that 66\% of the participants experience a problem from
cloning and reusing Stack Overflow snippets. Fifty-six percent of the visitors
never report the problems back to Stack Overflow. Lastly, 85\% of the
participants are not aware of CC BY-SA 3.0 license and 62\% never give
attributions to Stack Overflow posts or answers they copied the code from.
Moreover, 66\% of the participants do not check for licensing conflicts between
the cloned Stack Overflow code and their software. We suggest Stack Overflow to
raise an awareness of their users, both the answerers and the visitors, to the
problem of code obsolescence and licensing.
\end{abstract}

@@

\subsection{Survey Objective}
The main objective of the survey is to understand the developers' awareness and
experience to outdated code and code licensing on Stack Overflow. It can break
down into the following five research questions.

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
%	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ5 (Software license of Stack Overflow code snippets):}\textit{Are Stack Overflow visitors aware of code licensing on Stack Overflow}
\end{enumerate}

The first three questions will be answered by
the Stack Overflow answerer survey, while the other two questions will be
answered by the Stack Overflow visitor survey.

@@

\subsubsection{The visitor survey} 
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of
visiting Stack Overflow for solving programming tasks at least once. The
participants were invited to take the survey via five channels. The first
channel is via the first author's social media post (Facebook) where the he
invited friends who are software developers and have experience of copying code
snippets from Stack Overflow to take the survey. The second channel is a popular
technology news and media community in Thailand called \textsf{blognone.com} which
attracts a high number of Thai software developers. The first author posted an
invitation to the visitor survey in a discussion forum mentioning the
requirements to take the survey. The third channel collects answers from the
University of Molise from the help of an external researcher. The last two
channels are from a \textsf{comp.lang.java.programmer} Google groups and Software
Engineering Facebook page. The number of participants taken the survey is shown in
Table~\ref{tab:visitors}.

@@

\subsubsection*{Where do the developers search for programming solutions?}

@@

To sum up, Stack Overflow is ranked higher than official documentations, online
repositories, and book as the resource to look for programming solutions.
Developers rely on Stack Overflow answers because they are easy to search for on
the web. Moreover, 64\% of the participants reuse code snippets from Stack
Overflow at least once a week. The copy code from Stack Overflow because they
can be found easily from search engine, solve similar problems to their
problems, provide helpful context, and offer voting and accepted answers.

\subsubsection*{RQ4: What are the problems Stack Overflow visitors experiencing
	from reusing code snippets on Stack Overflow?}

@@

The problems from reusing Stack Overflow code snippets (illustrated in
Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions, i.e.~the
code claims to solve the problem in the question while it does not,  (28 out of
57 $\approx$ 49\% participants reported this); outdated solutions, i.e.~the code
may work with the some older versions of the library or API, but not the one
they are using, (39 out of 57 $\approx$ 68\% participants reported this);
mismatched solutions, i.e.~the code solves the problem in the question but it is
not exactly the right solution for their problem, (40 out of 57 $\approx$ 70\%
participants reported this); and buggy code (1 out of 57 $\approx$ 2\%
participants reported this).

Stack Overflow visitors rarely report the problems back to the discussion
threads (as can be seen in
Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32 participants
who encounter problems of Stack Overflow snippets, 18 of them (56\%) never
report the problems. Fourteen participants who reported the problems
did so by writing a comment (10), down-voting the answer (8), contacted the
answerer (2), and posting the new and correct answer (2), as shown in
Figure~\ref{fig:survey_visitor_how_report_problems}.

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2.2cm]{0.98\textwidth}{%
		\textit{For RQ4, our survey results show that 57 out of 87 Stack Overflow
			visitors find a problem from reusing Stack Overflow code snippets. Ten
			participants experience the problems from more than 80\% of the copied snippets and
			sixteen participants face the problems from 40--60\% of the reused code. The
			problems ranked by frequency include mismatched solutions (40), outdated
			solutions (39), incorrect solutions (28), and buggy code (1). Fifty-six percent
			of the participants never report the problems back to Stack Overflow.}}%
} \vspace{0.5cm}

\subsubsection*{RQ5: Are Stack Overflow visitors aware of code licensing on Stack Overflow?}

As depicted in Figure~\ref{fig:survey_visitor_cc_by-sa}, 74 out of 87 (85\%)
Stack Overflow visitors are not aware, at the time of copying the code, that
Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC
BY-SA 3.0) to content in the posts, including code snippets. As a consequence
62\% of the visitors never give an attribution, which is required by CC BY-SA
3.0, to a Stack Overflow post they copied the code from (the complete statistics
can be found from Figure~\ref{fig:survey_visitor_attribution-sa}).

@@

%\subsubsection*{RQ7: How often do Stack Overflow visitors check for software
%	licensing issues from code snippets on Stack Overflow?}

Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow
never check if the code snippet originated from a different source (e.g. an open
source project) with an incompatible license to their projects (see
Figure~\ref{fig:survey_visitor_original_license}).

Fifty seven participants (66\%) never check for licensing conflicts at all
when reusing Stack Overflow code (see
Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, possibly due
to their fairly small size of code which might fall under fair use, only 9\% of
the participants experience legal issues by reusing code snippets on Stack
Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}). Nonetheless, as we designed the
survey to be anonymous, it is not possible to contact them for further details
on the legal issues they found.

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1.7cm]{0.98\textwidth}{%
		\textit{For RQ5, 85\% of the participants are not aware of Stack Overflow CC
			BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
			they copied the code snippets from. We found that 66\% of the visitors never check for software
	licensing conflicts between Stack Overflow code snippets and their projects.
	However, only 9\% of the participants encountered legal issues.}}%
} \vspace{0.5cm}

@@

\subsection{Internal Validity}
Due to a large number of users on Stack Overflow, we could invite only 607
developers to participate in the answerer survey. If all the developers are
invited, which is almost impossible considering 7.6 million users on Stack
Overflow, the results may be different. Nevertheless, we mitigate this threat to
internal validity by selecting the participants based on their Stack Overflow
reputation. This targeted selection of the participants makes sure that we
invite developers who have been actively involved in asking and answering
questions on the site for a long period of time, and refrain from inviting new
users who merely answer a question or two. The highest reputation user invited
to our survey answered 33,933 questions and the lowest reputation user in our
survey answered 116 questions.

We selected the participants for the visitor survey based on convenient sampling
which could suffer from bias and outliers. We mitigate the threat by inviting
different groups of participants ranging from the author's social media,
technology news and media community, software engineering community (on
Facebook), Java programmer discussion thread (com.lang.java.programmer), and
from University of Molise.

\subsection{External Validity} 
While the reputation is a good proxy to reflect the amount of answers the
developers have given, it might not cover all kinds of answerers and their
experience on Stack Overflow. The answerers who have lower-reputation than 6,999
were not invited to our study and their awareness and experience may differ from
our findings. Hence, our findings may not be generalised to all Stack Overflow
answerers.

At least 39\% of the participants in the visitor survey are from Thailand
(\textsf{blognone.com} and some of the first author's contacts). Due to working
culture, answers from this group of developers may only represent software
developers in Thailand. Similarly our findings from the visitor survey may not
be generalised to all Stack Overflow visitors. We alleviate this concern by
inviting participants from other groups, e.g.~University of Molise in Italy,
comp.lang.java.programmer, and Software Engineering Facebook group.

@@

We present the results from online surveys of Stack Overflow answerers and
visitors regarding their awareness and experience of answering and reusing code
snippets on Stack Overflow. We are interested in cloned snippets in Stack Overflow
answers. Two online surveys have been performed to find out \textit{where} are
the code snippets in Stack Overflow answers from and \textit{how} developers, in
terms of both Stack Overflow answerers and visitors, handle potential problem of
outdated code and software licensing conflicts.

From the answerer's responses, we discovered that code in Stack Overflow answers
is usually written from scratch to answer a question. Nonetheless, there are
some code snippets that are copied from the answerer personal or company projects,
and open source software.

The outdated code on Stack Overflow occurs when the code snippet in an answer is
copied from another location and is no longer up-to-date. The results show that
although the answerers are aware of outdated code in their answers, 19\% of them
rarely or never fix the code. One answerer express a concern of having
outdated code in his/her popular answer (by having high Google rank) being used 
by many other developers.

Approximately 60\% of the answerers are aware of
Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
the license in their answers nor check for licensing conflicts when they copy
the code from another location and paste in the answer. Some developers believe
the code are too small and fall under fair use policy while others state the license
of their code in their profile pages instead.
